Adaptive Resolution Simulation in Equilibrium and Beyond

### 2015-02-25 writeDown/pub.epj/paper.tex
revised paper

Adaptive resolution simulation (AdResS)~\cite{praprotnik2005adaptive,praprotnik2006adaptive,praprotnik2007adaptive,praprotnik2008multiscale,poma2010classical,poblete2010coupling,praprotnik2011statistical,fritsch2012adaptive,bevc2013adaptive} is a concurrent multiscale simulation method for molecular system.
The terminology ``concurrent multiscale simulation'' means that
part of the system is simulated with higher resolution molecular models for the
purpose of accuracy, and \emph{in the meanwhile} the rest of the system is
simulated with lower resolution models for the purpose of saving computational cost.
AdResS is, therefore, suitable for the systems where different physical
phenomena is happening concurrently at different time and length scales. For example,
the structure of a protein and its solvation shell
should be resolved at the atomistic level, while far away form the protein,
only the hydrodynamic properties of the solvent are of interest, which can be studied with satisfactory
accuracy with very coarse-grained or even continuum
models~\cite{zavadlav2014adaptive,zavadlav2014adaptive1,delgado2009coupling}.
Similar  
techniques sharing the concurrent idea of multiscale simulation can be found, for example in Ref.~\cite{ensing2007energy,heyes2010thermodynamic,shi2006mixed,shen2014resolution,nielsen2010adaptive}.

The time evolution of a classical molecular systems
is modeled with Newtonian dynamics, and fundamental conservation laws
are satisfied, i.e.~the momentum and energy conservation.
However, in the AdResS system,
due to the spacial change of molecular resolution,
the two conservation laws cannot be satisfied in the same system~\cite{praprotnik2011comment,dellesite2007some}.
Traditionally, the AdResS scheme follows the \emph{force interpolation} approaches
that preserves the momentum conservation while breaks the energy
conservation.
Recently,
alternative approaches based on \emph{potential interpolation},
which preserve energy conservation while break the momentum conservation,
were designed~\cite{wang2013grand,potestio2013hamiltonian}.
The choice between the two AdResS branches therefore depends on the application. For example, in the
cases of studying hydrodynamics, the momentum conservation is preferred to the energy conservation.
However, if only the equilibrium properties are of interest,
the question should be asked on the ensemble that AdResS samples,
rather than directly on the mechanical conservation laws.
\recheck{It has been shown that, without the energy conservation, the force interpolation AdResS achieves
very high accuray in equilibrium properties such as the radial distribution function, three-body correlation and chemical potential~\cite{wang2013grand}.}
In this context,
it is worth noting that energy conservation is not a must for theoretical analyses on the equilibrium statistical properties,
although out of the energy conservation
one can define an auxiliary Hamiltonian~\cite{wang2013grand,agarwal2014chemical}
(not a physical one~\cite{dellesite2013multiscale}),
which reduces the mathematical difficulties.
In Sec.~\ref{sec:statistical} the force and potential interpolations are investigated 
under the same theoretical framework GC-AdResS (GC stands for ``Grand-Canonical like'')~\cite{wang2013grand} that raises necessary conditions
for a grand-canonical sampling with AdResS scheme.
In Sec.~\ref{sec:thermodynamic} the equilibrium thermodynamic relations between the resolutions are
provided for both branches of the AdResS.
From these relations, it is noticed that the absence of mechanical conservation laws 
modifies the way of thermodynamic equilibrium between the resolutions.

The GC-AdResS framework answers how to accurately compute the  equilibrium properties.
However, although the system is in equilibrium,
some properties, which are called dynamical properties,
\recheck{depend not only on the equilibrium ensemble, but also on the dynamics of the system.}
% cannot be simply computed from the equilibrium ensemble averages.
% These properties are called dynamical properties.
A typical example is the velocity auto-correlation\footnote{
  \recheck{
  The velocity auto-correlation
  % is the ensemble average
  % of the spontaneous fluctuation of the molecular velocity, being more precisly,
  is defined by the correlation between the velocity at a certain time and a time interval, e.g., $\Delta t$ later.
  It should be noted that
  the velocity auto-correlation depends on way that the system evolves in the time interval $\Delta t$,
  therefore, it is a dynamical property. }}.
% that describs the infiniesimal response of the system
% to external perturbation.
Moreover, the time-scales of conformational transformations
of bio-macromolecules (e.g.~protein and DNA)
are, again, dynamical properties.
The investigation of these  dynamical properties are out of the scope of the GC-AdResS framework,
and to the best of our knowledge, there is no theoretical answers on how accurately  AdResS reproduces the 
dynamical properties of a system.
Therefore, it is of practical significance to  provide numerical
evidence on the performance of AdResS in computing the dynamical properties.
In Sec.~\ref{sec:dynamical}, we investigate the
velocity auto-correlation in an AdResS water system, and the
leading relaxation time-scales and corresponding conformational dynamics of
a model dipeptide system.
The importance of designing the thermostat in these simulations
is also discussed.
The paper is closed by a concluding section
that mainly discusses the open problems in AdResS from both theoretical
and practical perspectives.

@@

In AdResS scheme, the simulation region $\Omega$ is 
decomposed without overlapping into three regions:
the atomistic region $\Omega_\AT$, the coarse-grained region $\Omega_\CG$, and
a hybrid region $\Omega_\HY$ bridging the former two regions.
That means the atomistic region is always connected to the coarse-grained region via a hybrid region.
The names of the atomistic and coarse-grained regions are self-explanatory, while
in the hybrid region each molecule has both the atomistic and coarse-grained resolutions.
A schematic plot of an AdResS simulation is presented in Fig.~\ref{fig:sys-region}.
The AdResS uses a scalar weighting function $w(\vect r),\ \vect r\in\Omega$ 
to denote the resolution of the molecule at position $\vect r$.
% In the atomistic region the value of the
% weighting function is usually set to 1, while in the coarse-grained
% region it is usually set to 0. In between, there is a bybrid region
% that is denoted by $\Omega_\HY$
% (or called transition region), where the molecules
% has both the atomistic and coarse-grained resolutions, and the weighting function
% goes smoothly from 1 to 0.
The definition of the weighting function
is not unique, one possible and perhaps the most popular choice is
\begin{equation}\label{eqn:old-w}
  w(\vect r) =
  \left\{
    \begin{alignedat}{3}
      &1 &\quad& \vect r \in \Omega_\AT\\
      &\cos^2\Big[\frac{\pi}{2 } \cdot \frac{\dist(\vect r, \Omega_\AT)}{d_\HY}\,\Big] && \vect r \in\Omega_\HY \\
      &0 &    & \vect r \in \Omega_\CG 
    \end{alignedat}
  \right.
\end{equation}
where $\dist(\vect r, \Omega_\AT)$ is the distance between the
position $\vect r$ and the atomistic region, which is defined
by $\dist(\vect r, \Omega_\AT) = \min_{\vect s\in\Omega_\AT} \vert
\vect r - \vect s \vert$.  $d_\HY$ is the thickness of the hybrid
region. We always assume the thickness of the hybrid region is
uniform, which indicates that the weighting function smoothly vanishes
at the boundary between the hybrid and the coarse-grained regions.
AdResS requires 
all interactions\footnote{The long-range electrostatic interactions
  are also treated by the cut-off method. \recheck{It is possible by using e.g.~the Reaction-Field method
  to calculate the electrostatic interactions.}
} being treated
by the cut-off method\footnote{\recheck{The general cut-off method is used
    in AdResS MD simulations.  The details of the cut-off method can be find in, e.g., Ref.~\cite{frenkel2001understanding}}}, and the thickness of
the hybrid region being at least one cut-off radius (denoted by $r_c$).
Moreover, owing to the double-resolution of hybrid molecules,
an atomistic molecule only interacts with the 
atomistic resolution of a hybrid molecule,
while a coarse-grained molecule only interacts with the coarse-grained resolution
of a hybrid molecule.
The atomistic molecules are thus not directly interacting with the coarse-grained molecules.
The benefit of these settings is that
there is no extra work for modeling the cross-scale interactions.

@@

The potential interpolation approach defines the hybrid energy by
\footnote{
\recheck{
  It worth noting that in Ref.~\cite{potestio2013hamiltonian} the potential interpolation is defined in a slightly different way:
  The product of the weighting functions $w_\moleidxone w_\moleidxtwo$ is replaced by the average average of them, i.e., $(w_\moleidxone + w_\moleidxtwo)/2$.}}
\begin{align}\label{eqn:v-v-interpol}
  {V}_{\moleidxone \moleidxtwo}=w_\moleidxone w_\moleidxtwo{V}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){V}^{\CG}_{\moleidxone\moleidxtwo}.
\end{align}
The intermolecular force is therefore calculated by taking the negative gradient on the potential ${\vect F}^V_{\moleidxone \moleidxtwo}= -\nabla_{\moleidxone}{V}_{\moleidxone \moleidxtwo}$,
which is explicitly written as
\begin{align}\label{eqn:f-v-interpol}
  {\vect F}^V_{\moleidxone \moleidxtwo}
  &=w_\moleidxone w_\moleidxtwo{\vect F}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){\vect F}^{\CG}_{\moleidxone\moleidxtwo}  - \nabla w_\moleidxone\cdot w_\moleidxtwo (V^\AT_{\moleidxone \moleidxtwo} - V^\CG_{\moleidxone \moleidxtwo})
\end{align}
Where $\nabla w_\moleidxone$ is the gradient of the weighting function measured at position $\vect r_\moleidxone$,
and the superscript ``$V$'' denotes that the force is defined
by the potential interpolation.
By  definition~\eqref{eqn:f-v-interpol}, the force of potential interpolation is conservative. 
The difference between the force and potential
interpolations lies in the last term  of Eq.~\eqref{eqn:f-v-interpol}, which is a force
acting along the direction of decreasing weighting function.
% This force is defined as \emph{the force of changing representation}.
It should be noted that
this force breaks the Newton's third law, therefore the force of potential interpolation
does not conserve the momentum.
We define the accumulative effect of this term by the \emph{force of changing representation}:
\begin{align}
  \vect F_\moleidxone^\rep = \sum_{\moleidxtwo}  \nabla w_\moleidxone\cdot w_\moleidxtwo (V^\AT_{\moleidxone \moleidxtwo} - V^\CG_{\moleidxone \moleidxtwo})
\end{align}

\begin{table}
  \centering
  \caption{A summary of the fundamental conservation laws in mechanics 
    satisfied by the normal molecular system and AdResS systems defined by force and potential interpolations.}
  \label{tab:conv-laws}
  \begin{tabular*}{0.8\textwidth}{@{\extracolsep{\fill}}lcc}\hline\hline
    &         Momentum Consv.     &       Energy Consv. \\
    Normal molecular System     &       {Yes}        &       {Yes}\\      
    AdResS force interpol.   &       {Yes}        &       {No}\\      
    AdResS potential interpol.  &     {No}  &       {Yes}\\\hline\hline
  \end{tabular*}
\end{table}
The fundamental conservation laws satisfied by both the force and potential interpolations
are summarized in Tab.~\ref{tab:conv-laws}. Unlike normal molecular systems, in which both
the momentum and energy are conserved, neither of the AdResS systems conserves
both laws. The breaks of these mechanics conservations have substantial influence on the thermodynamic
properties of the AdResS systems (see the discussions in Sec.~\ref{sec:thermodynamic}).
% The choice of the interpolation scheme depends on
% the practical requirement, for example, in hydrodynamic systems it is crucial to have the momentum
% conservation, then the force interpolation is prefered.
Regarding the equilibrium statistical properties, we will show later in Sec.~\ref{sec:statistical}
that both approaches approximately sample the grand-canonical ensemble.

When the intermolecular force is defined by either
Eq.~\eqref{eqn:f-f-interpol} or \eqref{eqn:f-v-interpol}, the total
force exerts on one molecule is the sum of all pairwise forces:
\begin{align}
  \vect F_\moleidxone = \sum_\moleidxtwo \vect F_{\moleidxone\moleidxtwo}, \quad \vect F^V_\moleidxone = \sum_\moleidxtwo \vect F^V_{\moleidxone\moleidxtwo}
\end{align}
The force on the atomistic degrees of freedom (DOFs) of a hybrid molecules is distributed 
by, 
\begin{align}
  \vect F_\atomidxone = \frac{m_\atomidxone}{M_\moleidxone}\vect F_\moleidxone, \quad   \vect F^V_\atomidxone = \frac{m_\atomidxone}{M_\moleidxone}\vect F^V_\moleidxone 
\end{align}
where  $\atomidxone$ is the indexes of atoms in molecule $\moleidxone$.
$m_\atomidxone$ is the mass of atom, and $M_\moleidxone$ is the total mass of molecule $\moleidxone$, i.e.~$M_\moleidxone = \sum_{\atomidxone\in\moleidxone}m_\atomidxone$.

Before discussing the statistical and thermodynamic properties of AdResS, a remark on the
choice of the weighting function should be added. 
In Ref.~\cite{wang2012adaptive} the authors introduced a modified weighing function with
a buffer region so that the atomistic region
interacts with the hybrid region only via the atomistic intermolecular interaction:
\begin{equation}\label{eqn:new-w}
  w(\vect r) =
  \left\{
    \begin{alignedat}{3}
      &1 &\quad& \vect r \in \Omega_\AT\\
      &1 && \vect r \in\Omega_\HY, \dist(\vect r, \Omega_\AT) < r_c \\
      &\cos^2\Big[\frac{\pi}{2 } \cdot \frac{\dist(\vect r, \Omega_\AT) - r_c}{d_{{\HY}} - r_c}\,\Big] && \vect r \in\Omega_\HY, \dist(\vect r, \Omega_\AT) \geq r_c\\
      &0 &    & \vect r \in \Omega_\CG 
    \end{alignedat}
  \right.
\end{equation}
The minimum thickness of the hybrid region is therefore $2r_c$.
It worth noting that the coarse-grained region does not require a buffer in the hybrid region, because
by definition the coarse-grained region interacts with the hybrid region only via the coarse-grained intermolecular interaction.
The new definition~\eqref{eqn:new-w} is crucial for the equilibrium statistical properties of the AdResS,
however, the extra cost is spent in the buffer $\{\vect r \vert \vect r \in\Omega_\HY, \dist(\vect r, \Omega_\AT) < r_c\}$,
which is treated in atomistic resolution. This cost is relatively small for systems with a large atomistic region.

@@

In order to consider the accuracy of the AdResS from statistical perspective, we always compare it with a full
atomistic reference system, which is of the same size as the AdResS system,
and contains the same number of molecules.
If the configuration of the atomistic region in the AdResS 
is same as the corresponding subregion in the atomistic reference, then
the AdResS  is of good accuracy (see the comparison indicated by the red arrow in Fig.~\ref{fig:compare}).
A well-known conclusion of the standard statistical mechanics is that
when the reference system approximates the thermodynamic limit, the subsystem
\recheck{samples} the grand-canonical ensemble. Therefore, it is natural to investigate
if the atomistic region of AdResS also \recheck{samples} the grand-canonical ensemble
in the same thermodynamic limit. The theoretical framework presented in this section works for
both the force and potential interpolations.

@@

We denote the number of molecules, volume and temperature of the system by $N$, $V$ and $T$, respectively.
The atomistic reference system has exactly the same set of variables, and its equilibrium state  is
the \emph{desired equilibrium} of AdResS.
% The word ``desired'' means that
% the atomistic region of the AdResS system should reproduce the equilibrium properties corresponding subregion of the reference
% system.
The thermodynamic variables of the subregions are specified by the subscript,
for example, those of the atomistic region are 
$N_\AT$, $V_\AT$ and $T_\AT$. Those of the hybrid and coarse-grained regions
are denoted by adding subscripts ``$\HY$'' and ``$\CG$'', respectively.
Identities $N = N_\AT + N_\HY + N_\CG$ and $V = V_\AT + V_\HY + V_\CG$ obviously hold
in the AdResS system.
In equilibrium, the temperature is uniform across the system: $T = T_\AT = T_\HY = T_\CG$.
This is achieved in practice by coupling the whole system to a Langevin thermostat.
The pressure and chemical potential of the atomistic and coarse-grained regions
are denoted by $\{p_\AT, \mu_\AT\}$
and $\{p_\CG, \mu_\CG\}$, respectively.
The DOFs of molecules indexed $\moleidxone$ are $\vect x_\moleidxone = \{\vect r_\moleidxone, \vect p_\moleidxone\}$, where
$\vect r_\moleidxone$ denotes the generalized coordinates and $\vect p_\moleidxone$ denotes the corresponding momenta.
All the DOFs of the system are denoted by $\vect x = \{\vect x_1, \cdots, \vect x_N\}$. Without lost of
generality, we consider that molecules index by $\{1, \cdots, N_\AT\}$ are in the atomistic region, then $\{N_\AT+1, \cdots, N_\AT + N_\HY\}$ are in the hybrid region, and
the last $N_\CG$ molecules $\{N-N_\CG+1, \cdots, N\}$ are in the coarse-grained region. The corresponding DOFs are denoted by $\vect x_\AT$, $\vect x_\HY$ and $\vect x_\CG$.
It should be noted that for simplicity, we do not explicitly consider that the number of DOFs are different for an atomistic
and a coarse-grained molecule, and uniformly encode them by the vector $\vect x$.
% so it is acutally 
% \redc{The atomistic, hybrid and coarse-grained have different DOFs, a comment needed!}

@@

The accuracy of number probability $p(N_\AT)$ is investigated by a
Taylor expansion w.r.t.~the relative size of the atomistic region to
the whole system, which vanishes in the thermodynamic limit. The sufficient condition for the first order accuracy
asks for a balance of the chemical potential~\cite{wang2013grand}:
\begin{align}\label{eqn:mu-eq}
  \mu_\CG - \mu_\AT = \omega_0,
\end{align}
where $\omega_0$ corresponds to the work from the filter on each
molecule that leaves the coarse-grained region and  enters the atomistic region. An important conclusion
form Ref.~\cite{wang2013grand} is that the relation~\eqref{eqn:mu-eq}
holds automatically when the thermodynamic force is applied so that the atomistic
and coarse-grained densities match. The conclusion is derived under
the assumption of thermodynamic limit and the decorrelation between the
atomistic and coarse-grained regions.

>>>>

Adaptive resolution simulation (AdResS)~\cite{praprotnik2005adaptive,praprotnik2006adaptive,praprotnik2007adaptive,praprotnik2008multiscale,poma2010classical,poblete2010coupling,praprotnik2011statistical,fritsch2012adaptive,bevc2013adaptive} is a concurrent multiscale simulation method for molecular systems.
The terminology ``concurrent multiscale simulation'' means that
part of the system is simulated with higher resolution molecular models for the
purpose of accuracy, and \emph{in the meanwhile} the rest of the system is
simulated with lower resolution models for the purpose of saving computational cost.
AdResS is, therefore, suitable for the systems where different physical
phenomena is happening concurrently at different time and length scales. For example,
the structure of a protein and its solvation shell
should be resolved at the atomistic level, while far away from the protein,
only the hydrodynamic properties of the solvent are of interest, which can be studied with satisfactory
accuracy with very coarse-grained or even continuum
models~\cite{zavadlav2014adaptive,zavadlav2014adaptive1,delgado2009coupling}.
Similar  
techniques sharing the concurrent idea of multiscale simulation can be found, for example in Ref.~\cite{ensing2007energy,heyes2010thermodynamic,shi2006mixed,shen2014resolution,nielsen2010adaptive}.

The time evolution of a classical molecular system
is modeled with Newtonian dynamics, and fundamental conservation laws
are satisfied, i.e.~the momentum and energy conservation.
However, in the AdResS system,
due to the spacial change of molecular resolution,
the two conservation laws cannot be satisfied at the same time~\cite{praprotnik2011comment,dellesite2007some}.
Traditionally, the AdResS scheme follows the \emph{force interpolation} approaches
that preserves the momentum conservation while breaking the energy
conservation.
Recently,
alternative approaches based on \emph{potential interpolation},
which preserve energy conservation while breaking the momentum conservation,
were designed~\cite{wang2013grand,potestio2013hamiltonian}.
The choice between the two AdResS branches therefore depends on the application. For example, in the
cases of studying hydrodynamics, the momentum conservation is preferred to the energy conservation.
However, if only the equilibrium properties are of interest,
the question should be asked on the ensemble that AdResS samples,
rather than directly on the mechanical conservation laws.
\recheck{It has been shown that, without the energy conservation, the force interpolation AdResS achieves
very high accuracy in equilibrium properties, such as the radial distribution function, the three-body correlation and the chemical potential~\cite{wang2013grand}.}
In this context,
it is worth noting that energy conservation is not a must for theoretical analyses on the equilibrium statistical properties,
although out of the energy conservation
one can define an auxiliary Hamiltonian~\cite{wang2013grand,agarwal2014chemical}
(not a physical one~\cite{dellesite2013multiscale}),
which reduces the mathematical difficulties.
In Sec.~\ref{sec:statistical} the force and potential interpolations are investigated 
under the same theoretical framework GC-AdResS (GC stands for ``Grand-Canonical like'')~\cite{wang2013grand} that raises necessary conditions
for a grand-canonical sampling with AdResS scheme.
In Sec.~\ref{sec:thermodynamic} the equilibrium thermodynamic relations between the resolutions are
provided for both branches of the AdResS.
From these relations, it is noticed that the absence of mechanical conservation laws 
modifies the way of thermodynamic equilibrium between the resolutions.

The GC-AdResS framework answers how to accurately compute the  equilibrium properties.
However, although the system is in equilibrium,
some properties, which are called dynamical properties,
\recheck{depend not only on the equilibrium ensemble, but also on the dynamics of the system.}
% cannot be simply computed from the equilibrium ensemble averages.
% These properties are called dynamical properties.
A typical example is the velocity auto-correlation\footnote{
  \recheck{
  The velocity auto-correlation
  % is the ensemble average
  % of the spontaneous fluctuation of the molecular velocity, being more precisly,
  is defined by the correlation between the velocity at a certain time and a time interval, e.g., $\Delta t$ later.
  It should be noted that
  the velocity auto-correlation depends on way that the system evolves in the time interval $\Delta t$,
  therefore, it is a dynamical property. }}.
% that describs the infiniesimal response of the system
% to external perturbation.
Moreover, the time-scales of conformational transformations
of bio-macromolecules (e.g.~protein and DNA)
are, again, dynamical properties.
The investigation of these  dynamical properties are out of the scope of the GC-AdResS framework and,
to the best of our knowledge, there is no theoretical answer on how accurately  AdResS reproduces the 
dynamical properties of a system.
Therefore, it is of practical significance to  provide numerical
evidence on the performance of AdResS in computing the dynamical properties.
In Sec.~\ref{sec:dynamical}, we investigate the
velocity auto-correlation in an AdResS water system, and the
leading relaxation time-scales and corresponding conformational dynamics of
a model dipeptide system.
The importance of designing the thermostat in these simulations
is also discussed.
The paper is closed by a concluding section
that mainly discusses the open problems in AdResS from both theoretical
and practical perspectives.

@@

In AdResS scheme, the simulation region $\Omega$ is 
decomposed without overlapping into three regions:
the atomistic region $\Omega_\AT$, the coarse-grained region $\Omega_\CG$, and
a hybrid region $\Omega_\HY$ bridging the former two regions.
That means the atomistic region is always connected to the coarse-grained region via a hybrid region.
The names of the atomistic and coarse-grained regions are self-explanatory, while
in the hybrid region each molecule has both the atomistic and coarse-grained resolutions.
A schematic plot of an AdResS simulation is presented in Fig.~\ref{fig:sys-region}.
The AdResS uses a scalar weighting function $w(\vect r),\ \vect r\in\Omega$ 
to denote the resolution of the molecule at position $\vect r$.
% In the atomistic region the value of the
% weighting function is usually set to 1, while in the coarse-grained
% region it is usually set to 0. In between, there is a bybrid region
% that is denoted by $\Omega_\HY$
% (or called transition region), where the molecules
% has both the atomistic and coarse-grained resolutions, and the weighting function
% goes smoothly from 1 to 0.
The definition of the weighting function
is not unique, one possible and perhaps the most popular choice is
\begin{equation}\label{eqn:old-w}
  w(\vect r) =
  \left\{
    \begin{alignedat}{3}
      &1 &\quad& \vect r \in \Omega_\AT\\
      &\cos^2\Big[\frac{\pi}{2 } \cdot \frac{\dist(\vect r, \Omega_\AT)}{d_\HY}\,\Big] && \vect r \in\Omega_\HY \\
      &0 &    & \vect r \in \Omega_\CG 
    \end{alignedat}
  \right.
\end{equation}
where $\dist(\vect r, \Omega_\AT)$ is the distance between the
position $\vect r$ and the atomistic region, which is defined
by $\dist(\vect r, \Omega_\AT) = \min_{\vect s\in\Omega_\AT} \vert
\vect r - \vect s \vert$.  $d_\HY$ is the thickness of the hybrid
region. We always assume the thickness of the hybrid region to be
uniform, which indicates that the weighting function smoothly vanishes
at the boundary between the hybrid and the coarse-grained regions.
AdResS requires 
all interactions\footnote{The long-range electrostatic interactions
  are also treated by the cut-off method. \recheck{It is possible by using e.g.~the Reaction-Field method~\cite{onsager1936electric,tironi1995generalized}
  to calculate the electrostatic interactions.}
} being treated
by the cut-off method\footnote{\recheck{AdResS uses the same general cut-off method as in normal MD simulations~\cite{frenkel2001understanding}.}}, and the thickness of
the hybrid region being at least one cut-off radius (denoted by $r_c$).
Moreover, owing to the double-resolution of hybrid molecules,
an atomistic molecule only interacts with the 
atomistic resolution of a hybrid molecule,
while a coarse-grained molecule only interacts with the coarse-grained resolution
of a hybrid molecule.
The atomistic molecules are thus not directly interacting with the coarse-grained molecules.
The benefit of these settings is that
there is no extra work for modeling the cross-scale interactions.

@@

The potential interpolation approach defines the hybrid energy by
\footnote{
\recheck{
  It worth noting that in Ref.~\cite{potestio2013hamiltonian} the potential interpolation is defined in a slightly different way:
  The product of the weighting functions $w_\moleidxone w_\moleidxtwo$ is replaced by the average average of them, i.e., $(w_\moleidxone + w_\moleidxtwo)/2$.}}
\begin{align}\label{eqn:v-v-interpol}
  {V}_{\moleidxone \moleidxtwo}=w_\moleidxone w_\moleidxtwo{V}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){V}^{\CG}_{\moleidxone\moleidxtwo}.
\end{align}
The intermolecular force is therefore calculated by taking the negative gradient on the potential ${\vect F}^V_{\moleidxone \moleidxtwo}= -\nabla_{\moleidxone}{V}_{\moleidxone \moleidxtwo}$,
which is explicitly written as
\begin{align}\label{eqn:f-v-interpol}
  {\vect F}^V_{\moleidxone \moleidxtwo}
  &=w_\moleidxone w_\moleidxtwo{\vect F}_{\moleidxone\moleidxtwo}^{\AT}+(1-w_\moleidxone w_\moleidxtwo){\vect F}^{\CG}_{\moleidxone\moleidxtwo}  - \nabla w_\moleidxone\cdot w_\moleidxtwo (V^\AT_{\moleidxone \moleidxtwo} - V^\CG_{\moleidxone \moleidxtwo})
\end{align}
Where $\nabla w_\moleidxone$ is the gradient of the weighting function measured at position $\vect r_\moleidxone$,
and the superscript ``$V$'' denotes that the force is defined
by the potential interpolation.
By  definition~\eqref{eqn:f-v-interpol}, the force of the potential interpolation is conservative. 
The difference between the force and potential
interpolations lies in the last term  of Eq.~\eqref{eqn:f-v-interpol}, which is a force
acting along the direction of decreasing weighting function.
% This force is defined as \emph{the force of changing representation}.
It should be noted that
this force breaks the Newton's third law, therefore the force of potential interpolation
does not conserve the momentum.
We define the cumulative effect of this term by the \emph{force of changing representation}:
\begin{align}
  \vect F_\moleidxone^\rep = \sum_{\moleidxtwo}  \nabla w_\moleidxone\cdot w_\moleidxtwo (V^\AT_{\moleidxone \moleidxtwo} - V^\CG_{\moleidxone \moleidxtwo})
\end{align}

\begin{table}
  \centering
  \caption{A summary of the fundamental conservation laws in mechanics 
    satisfied by the normal molecular system and AdResS systems defined by force and potential interpolations.}
  \label{tab:conv-laws}
  \begin{tabular*}{0.8\textwidth}{@{\extracolsep{\fill}}lcc}\hline\hline
    &         Momentum Consv.     &       Energy Consv. \\
    Normal molecular System     &       {Yes}        &       {Yes}\\      
    AdResS force interpol.   &       {Yes}        &       {No}\\      
    AdResS potential interpol.  &     {No}  &       {Yes}\\\hline\hline
  \end{tabular*}
\end{table}
The fundamental conservation laws satisfied by both the force and potential interpolations
are summarized in Tab.~\ref{tab:conv-laws}. Unlike normal molecular systems, in which both
the momentum and energy are conserved, neither of the AdResS systems conserves
both laws. The breaking of these mechanics conservations has substantial influence on the thermodynamic
properties of the AdResS systems (see the discussions in Sec.~\ref{sec:thermodynamic}).
% The choice of the interpolation scheme depends on
% the practical requirement, for example, in hydrodynamic systems it is crucial to have the momentum
% conservation, then the force interpolation is prefered.
Regarding the equilibrium statistical properties, we will show later in Sec.~\ref{sec:statistical}
that both approaches approximately sample the grand-canonical ensemble.

When the intermolecular force is defined by either
Eq.~\eqref{eqn:f-f-interpol} or \eqref{eqn:f-v-interpol}, the total
force exerts on one molecule is the sum of all pairwise forces:
\begin{align}
  \vect F_\moleidxone = \sum_\moleidxtwo \vect F_{\moleidxone\moleidxtwo}, \quad \vect F^V_\moleidxone = \sum_\moleidxtwo \vect F^V_{\moleidxone\moleidxtwo}
\end{align}
The force on the atomistic degrees of freedom (DOFs) of a hybrid molecule is distributed 
by, 
\begin{align}
  \vect F_\atomidxone = \frac{m_\atomidxone}{M_\moleidxone}\vect F_\moleidxone, \quad   \vect F^V_\atomidxone = \frac{m_\atomidxone}{M_\moleidxone}\vect F^V_\moleidxone 
\end{align}
where  $\atomidxone$ is the index of an atom in molecule $\moleidxone$.
$m_\atomidxone$ is the mass of atom $\alpha$, and $M_\moleidxone$ is the total mass of molecule $\moleidxone$, i.e.~$M_\moleidxone = \sum_{\atomidxone\in\moleidxone}m_\atomidxone$.

Before discussing the statistical and thermodynamic properties of AdResS, a remark on the
choice of the weighting function should be added. 
In Ref.~\cite{wang2012adaptive} the authors introduced a modified weighting function with
a buffer region so that the atomistic region
interacts with the hybrid region only via the atomistic intermolecular interaction:
\begin{equation}\label{eqn:new-w}
  w(\vect r) =
  \left\{
    \begin{alignedat}{3}
      &1 &\quad& \vect r \in \Omega_\AT\\
      &1 && \vect r \in\Omega_\HY, \dist(\vect r, \Omega_\AT) < r_c \\
      &\cos^2\Big[\frac{\pi}{2 } \cdot \frac{\dist(\vect r, \Omega_\AT) - r_c}{d_{{\HY}} - r_c}\,\Big] && \vect r \in\Omega_\HY, \dist(\vect r, \Omega_\AT) \geq r_c\\
      &0 &    & \vect r \in \Omega_\CG 
    \end{alignedat}
  \right.
\end{equation}
The minimum thickness of the hybrid region is therefore $2r_c$.
It is worth noting that the coarse-grained region does not require a buffer in the hybrid region, because
by definition the coarse-grained region interacts with the hybrid region only via the coarse-grained intermolecular interaction.
The new definition~\eqref{eqn:new-w} is crucial for the equilibrium statistical properties of the AdResS,
however, the extra cost is spent in the buffer $\{\vect r \vert \vect r \in\Omega_\HY, \dist(\vect r, \Omega_\AT) < r_c\}$,
which is treated in atomistic resolution. This cost is relatively small for systems with a large atomistic region.

@@

In order to consider the accuracy of the AdResS from a statistical perspective, we always compare it with a full
atomistic reference system, which is of the same size as the AdResS system,
and contains the same number of molecules.
If the configuration of the atomistic region in the AdResS 
is the same as that of the corresponding subregion in the atomistic reference, then
the AdResS  is of good accuracy (see the comparison indicated by the red arrow in Fig.~\ref{fig:compare}).
A well-known conclusion of the standard statistical mechanics is that
when the reference system approximates the thermodynamic limit, the subsystem
\recheck{samples} the grand-canonical ensemble. Therefore, it is natural to investigate
if the atomistic region of AdResS also \recheck{samples} the grand-canonical ensemble
in the same thermodynamic limit. The theoretical framework presented in this section works for
both the force and potential interpolations.

@@

We denote the number of molecules, volume and temperature of the system by $N$, $V$ and $T$, respectively.
The atomistic reference system has exactly the same set of variables, and its equilibrium state  is
the \emph{desired equilibrium} of AdResS.
% The word ``desired'' means that
% the atomistic region of the AdResS system should reproduce the equilibrium properties corresponding subregion of the reference
% system.
The thermodynamic variables of the subregions are specified by the subscript,
for example, those of the atomistic region are 
$N_\AT$, $V_\AT$ and $T_\AT$. Those of the hybrid and coarse-grained regions
are denoted by adding subscripts ``$\HY$'' and ``$\CG$'', respectively.
Identities $N = N_\AT + N_\HY + N_\CG$ and $V = V_\AT + V_\HY + V_\CG$ obviously hold
in the AdResS system.
In equilibrium, the temperature is uniform across the system: $T = T_\AT = T_\HY = T_\CG$.
This is achieved in practice by coupling the whole system to a Langevin thermostat.
The pressure and chemical potential of the atomistic and coarse-grained regions
are denoted by $\{p_\AT, \mu_\AT\}$
and $\{p_\CG, \mu_\CG\}$, respectively.
The DOFs of molecules indexed $\moleidxone$ are $\vect x_\moleidxone = \{\vect r_\moleidxone, \vect p_\moleidxone\}$, where
$\vect r_\moleidxone$ denotes the generalized coordinates and $\vect p_\moleidxone$ denotes the corresponding momenta.
All the DOFs of the system are denoted by $\vect x = \{\vect x_1, \cdots, \vect x_N\}$. Without loss of
generality, we consider that molecules index by $\{1, \cdots, N_\AT\}$ are in the atomistic region, then $\{N_\AT+1, \cdots, N_\AT + N_\HY\}$ are in the hybrid region, and
the last $N_\CG$ molecules $\{N-N_\CG+1, \cdots, N\}$ are in the coarse-grained region. The corresponding DOFs are denoted by $\vect x_\AT$, $\vect x_\HY$ and $\vect x_\CG$.
It should be noted that for simplicity, we do not explicitly consider that the number of DOFs are different for an atomistic
and a coarse-grained molecule, and uniformly encode them by the vector $\vect x$.
% so it is acutally 
% \redc{The atomistic, hybrid and coarse-grained have different DOFs, a comment needed!}

@@

The accuracy of number probability $p(N_\AT)$ is investigated by a
Taylor expansion w.r.t.~the relative size of the atomistic region to
the whole system, which vanishes in the thermodynamic limit. The sufficient condition for the first order accuracy
asks for a balance of the chemical potential~\cite{wang2013grand}:
\begin{align}\label{eqn:mu-eq}
  \mu_\CG - \mu_\AT = \omega_0,
\end{align}
where $\omega_0$ corresponds to the work from the filter on each
molecule that leaves the coarse-grained region and  enters the atomistic region. An important conclusion
from Ref.~\cite{wang2013grand} is that the relation~\eqref{eqn:mu-eq}
holds automatically when the thermodynamic force is applied so that the atomistic
and coarse-grained densities match. The conclusion is derived under
the assumption of thermodynamic limit and the decorrelation between the
atomistic and coarse-grained regions.
